Designing Types for R, Empirically

### 2020-05-16 paper/main.tex
types

>>>>

type `stabledist::x.exp.m.x` <double[]> => double[];

type `lava::index` <class<`lvm`> | class<`lvmfit`>, ...> => (null | list<any>);

type `pkgload::compact` <list<any>> => list<any>;

type `diptest::dip` <double[], character | logical, logical, double> => (class<`dip`> | double);

type `bbmle::relist2` <double[], double[] | list<any>> => list<any>;

type `stabledist::cospi2` <double[]> => double[];
type `stabledist::tanpi2` <double[]> => double[];

type `neuralnet::relist` <double[], class<`array`> | integer[], class<`array`> | integer[]> => list<class<`matrix`>>;
type `neuralnet::calculate.gradients` <any, integer, list<class<`matrix`>>, any, class<`matrix`>, double, logical> => double[];
